---
title             : "Reproducing the Report of "
shorttitle        : "Something Analyis"

author: 
  - name          : "Shawn Vizganr"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "2900 Bedford Avenue"
    email         : "sv942@hunter.cuny.edu"
    
  
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Brooklyn College City University of New York"

authornote: |
 Current Undergraduate at Brooklyn college, nothing special here

abstract: |
This is a reanalysis of the first experiment of something something baby voice recognition
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "sound, babies"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)


```
#Abstract
This is a reproduction of experiment 1 of For 5-Month-Old Infants, Melodies Are Social" by Samuel A. Mehr, Lee Ann Song, Elizabeth S. Spelke. In their experiment, they had the parents of 32 infants learn a song and later sing it to their children.On a later date the babies attention was tracked for how long they focused on the song their parents sang or a novel song, both songs being sung by an unfamiliar person. Results found that Babies spent more time looking at people who sang familiar songs than those who didn't.
#Introduction
The purpose of this (re)-analysis is to see whether or not it is possible to reproduce the results of experiment 1 of "For 5-Month-Old Infants, Melodies Are Social" by Samuel A. Mehr, Lee Ann Song, Elizabeth S. Spelke.


## Participants

There were 32 participants

## Material

The details of the experiment are reported in Mehr SA 2016

## Procedure

Parents were taught a song at the lab, and they would sing it to their children. At the lab, children were later introduced to two novel people over a screen, one who sang the sang they knew and one who didn', both of which were on screens that had recorded video of both singing their respective songs. Children were tracked for who they stared at longer. 

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results



# Discussion


\newpage

# References

  
    1. Mehr SA, Song LA, Spelke ES. For 5-Month-Old Infants, Melodies Are Social. Psychological Science. 2016;27(4):486-501. doi:10.1177/0956797615626691 https://journals-sagepub-com.ez-proxy.brooklyn.cuny.edu/doi/full/10.1177/0956797615626691#_i2
  


\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
